Working with Math environments in texor

### 2023-08-10 supplement/math-env/math-example.tex
Updated math supplement with custom commands.

The core of the MathJax project is the development of its state-of-the-art, open source, JavaScript platform for display of mathematics. The key design goals are \citep{mathjax}:
\begin{itemize}
    \item High-quality display of mathematics notation in all browsers.
    \item No special browser setup required.
    \item Support for LaTeX, MathML, and other equation markup directly in the HTML source.
    \item An extensible, modular design with a rich API for easy integration into web applications.
    \item Support for accessibility, copy and paste, and other rich functionality.
    \item Interoperability with other applications and math-aware search.
    \item Support for equation conversion outside a browser (e.g., preprocessing on a server).
\end{itemize}

@@

\begin{verbatim}
\begin{align}
f(x) = \frac{1}{\sigma\sqrt{2\pi}} 
  \exp\left( -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}\,\right)
  \label{eq:1}
\end{align}
\end{verbatim}
This will render as \ref{eq:1}.
\begin{align}
f(x) = \frac{1}{\sigma\sqrt{2\pi}} 
  \exp\left( -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}\,\right)
  \label{eq:1}
\end{align}

\section{Equation Numbering}
In LaTeX your equations get numbered automatically unless you are using \verb|\[..\]| to describe
math. Equation numbering works a bit differently in \CRANpkg{bookdown} (the base of RJ web article format) where
it is mandatory to have a \verb|(\#eq:xx)| which is described in more detail in \citep{bookdown}.

@@

\begin{align}
S_{T, s}(z_t) = & X^{\top} K_{b,t}^* X (Z - z_t)^s 
\label{eq:xe}
\end{align}

@@

@@

Altough MathJax does a good job of supporting most LaTeX math functions,
some functions do not work like \verb|\bm| \verb|\boldmath|, instead use \verb|\mathbb|.
Also avoid custom math commands MathJaX will never be able to parse it. The reason being
MathJax renders math case by case and custom commands will already be removed by pandoc
during the conversion, hence MathJax will not be aware of such redefinations.

@@

\bibitem[Krewinkel, Lucero (2023)]{pandoc}
A.~ Krewinkel and A.~ Lucero
\newblock pandoc 3.0 Release notes
\newblock \emph{pandoc} \penalty0 2023
\newblock URL \url{https://pandoc.org/releases.html#pandoc-3.0-2023-01-18}

\bibitem[Mathjax authors (2021)]{mathjax}
MathJax authors
\newblock Mathjax website
\newblock  \penalty0 2021
\newblock URL \url{https://www.mathjax.org/#features}

\bibitem[Yihui (2023)]{bookdown}
Yihui Xie
\newblock bookdown: Authoring Books and Technical Documents with R Markdown
\newblock \penalty0 2023
\newblock URL \url{https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#equations}

>>>>

The core goal of the MathJax project is the development of its state-of-the-art, open source, JavaScript platform for display of mathematics. The key design goals are \citep{mathjax}:
\begin{itemize}
    \item High-quality display of mathematics notation in all browsers.
    \item No special browser setup required.
    \item Support for LaTeX, MathML, and other equation markup directly in the HTML source.
    \item An extensible, modular design with a rich API for easy integration into web applications.
    \item Support for accessibility, copy and paste, and other rich functionality.
    \item Interoperability with other applications and math-aware search.
    \item Support for equation conversion outside a browser (e.g., preprocessing on a server).
\end{itemize}

@@

\begin{verbatim}
\begin{align}
f(x) = \frac{1}{\sigma\sqrt{2\pi}} 
  \exp\left( -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}\,\right)
  \label{eq:1}
\end{align}
\end{verbatim}
This will render as \ref{eq:1}.

\begin{align}
\label{eq:1}
f(x) = \frac{1}{\sigma\sqrt{2\pi}} 
  \exp\left( -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}\,\right)
\end{align}

\section{Equation Numbering}
In LaTeX your equations get numbered automatically unless you are using \verb|\[..\]| environment or \verb|\nonumber| to suppress
numbering. Equation numbering works a bit differently in \CRANpkg{bookdown} (the base of RJ web article format) where
it is mandatory to have a \verb|(\#eq:xx)| which is described in more detail in \citep{bookdown}.

@@

\begin{align}
S_{T, s}(z_t) = X^{\top} K_{b,t}^* X (Z - z_t)^s, 
\label{eq:xe}
\end{align}

@@

\section{Custom Math Commands}

%Also avoid custom math commands MathJaX will never be able to parse it. The reason being
%MathJax renders math case by case and custom commands will already be removed by pandoc
%during the conversion, hence MathJax will not be aware of such redefinations.
To ease the frequent use of the command, some custom math commands that contain LaTeX math commands. 
However, This will not function if you use functions/environments from CTAN packages or 
the ones that are out-of-the-box functions which do not render in HTML/markdown.

\paragraph{Acceptable}

\begin{verbatim}
\newcommand{\ABS}[1]{|#1|}
\end{verbatim}

$$ \ABS{\sigma^2} = \pm 1 $$

\paragraph{Not acceptable}

\begin{verbatim}
\newcommand{\rotatethis}[1]{\rotatebox[origin=c]{90}{$#1$}}
\end{verbatim}

$$ \rotatethis{\sigma^2} = \pm 1 $$

@@

Altough MathJax does a good job of supporting most LaTeX math functions,
some functions do not work like \verb|\bm| \verb|\boldmath|, instead use \verb|\mathbf|.

@@

\bibitem[Krewinkel, Lucero (2023)]{pandoc}
A.~ Krewinkel and A.~ Lucero
\newblock pandoc 3.0 Release notes
\newblock \emph{pandoc} \penalty0 2023
\newblock URL \url{https://pandoc.org/releases.html}

\bibitem[Mathjax authors (2021)]{mathjax}
MathJax authors
\newblock Mathjax website
\newblock  \penalty0 2021
\newblock URL \url{https://www.mathjax.org/}

\bibitem[Yihui (2023)]{bookdown}
Yihui Xie
\newblock bookdown: Authoring Books and Technical Documents with R Markdown
\newblock \penalty0 2023
\newblock URL \url{https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html}
